\ifx\pdfoutput\undefined % We're not running pdftex
\else
\pdfbookmark{Title Page}{title}
\fi
\newlength{\centeroffset}
\setlength{\centeroffset}{-0.5\oddsidemargin}
\addtolength{\centeroffset}{0.5\evensidemargin}
%\addtolength{\textwidth}{-\centeroffset}
\thispagestyle{empty}
\vspace*{\stretch{1}}
\noindent\hspace*{\centeroffset}\makebox[0pt][l]{\begin{minipage}{\textwidth}
\flushright
{\Huge\bfseries \XCDR\ -- User Guide}

\noindent\rule[-1ex]{\textwidth}{5pt}\\[2.5ex]
\hfill\emph{\Large Concepts and Highlevel Specification}
\end{minipage}}

\vspace{\stretch{1}}
\noindent\hspace*{\centeroffset}\makebox[0pt][l]{\begin{minipage}{\textwidth}
\flushright
{\bfseries Author:} Thomas D. Marsh\\[1.5ex]
\end{minipage}}

%\addtolength{\textwidth}{\centeroffset}
\vspace{\stretch{2}}


\pagebreak
\begin{small}
  Copyright \copyright 2003 Thomas D. Marsh.  All rights reserved.

\bigskip

  Please address your comments and suggestions to thomas.marsh@seznam.cz.

  Changes may be made periodically to the information in this publication.
  Such changes will be incorporated in new editions of this guide. The
  software described in this document is furnished under a license
  agreement and may be used or copied only in accordance with the terms
  of the license agreement. It is against the law to copy the software on any
  other medium except as specifically allowed in the license agreement. The
  licensee may make once copy of the software for backup purposes. No
  part of this publication may be reproduced, stored in a retrieval system, or
  transmitted in any form or by any means, electronic, mechanical,
  photocopy, recording, or otherwise, without the prior written permission of
  the copyright holders.

  The software license and limited warranty for the accompanying product
  are set forth in the information packet supplied with the product and is
  incorporated herein by this reference. If you can't locate the software
  license, contact your representative for a copy.

  All product names mentioned in this manual are for identification purpose
  only and are either trademarks or registered trademarks of their respective
  owners.
\end{small}


\endinput
